CommonMind Consortium: DLPFC

### 2020-09-20 combined_analysis/diff.networks.Rmd
Update diff networks

library(WGCNA)
library(variancePartition)
library(decorate)
library(ggrepel)
library(cowplot) 
library(zenith) 
library(knitr) 
library(plyr) 
library(qvalue)  
library(BiocParallel)  
}) 
source("../common_functions/common_functions.R")   
# source("common_functions/common_functions.R")

@@

# Null network
```{r diff.networks.null}

@@

	# Hypothesis testing         
	df_test = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA, useSLED=FALSE)

@@

fit_perm_null = beta.mle(p)

calc_p = function(p, fit){
	pbeta(p, 	shape1=fit_perm_null$param['alpha'], 
				shape2=fit_perm_null$param['beta'], 
				lower.tail=TRUE)
}

p = df_test$P.Value[df_test$Cohort== "NIMH-HBCC"]
data.frame("# DE" = sum(p.adjust(p, 'fdr') < 0.05) / length(p), check.names=FALSE) %>% kable
hist(p, main="P-values under the null in the replication cohort", xlab="p-value")
```

@@

```{r testing}
# Hypothesis testing         
df_test.Sex = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Sex, METADATA)#, BPPARAM=SnowParam(18)) 
```

@@

```{r testing.Dx}
# Hypothesis testing     
df_test.Dx = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Dx, METADATA)  
```

>>>>

library(WGCNA)
library(variancePartition)
library(decorate)
library(ggrepel)
library(cowplot) 
library(metap) 
library(zenith) 
library(knitr) 
library(plyr) 
library(qvalue)  
library(BiocParallel)  
})   
source("../common_functions/common_functions.R")   
# source("common_functions/common_functions.R")

@@

# Null permuations
```{r diff.networks.null}

@@

	# Hypothesis testing         
	df_test = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA, variable, useSLED=TRUE)

@@

beta_perm = list()
beta_perm[['MSSM-Penn-Pitt']] = beta.mle(p)

calc_p = function(p, fit){
	pbeta(p, 	shape1=fit$param['alpha'], 
				shape2=fit$param['beta'], 
				lower.tail=TRUE)
}

p = df_test$P.Value[df_test$Cohort== "NIMH-HBCC"]
data.frame("# DE" = sum(p.adjust(p, 'fdr') < 0.05) / length(p), check.names=FALSE) %>% kable
hist(p, main="P-values under the null in the replication cohort", xlab="p-value")

beta_perm[['NIMH-HBCC']] = beta.mle(p)
```

# Null permuations
```{r diff.networks.null}

METADATA$rnd = sample(c('A','B'), nrow(METADATA), replace=TRUE)
METADATA$rnd = factor(METADATA$rnd, c('A','B'))

# Hypothesis testing         
df_test_null = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors, METADATA, variable, useSLED=TRUE) 
```

@@

```{r testing}
# Hypothesis testing         
df_test.Sex = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Sex, METADATA, variable, useSLED=TRUE)
```

```{r test, eval=FALSE}
df2 = lapply( unique(df_test$Cohort), function(chrt){
	df = df_test[df_test$Cohort == chrt,]
	df$P.Value = calc_p(df$P.Value, beta_perm[[chrt]])
	df$FDR = p.adjust(df$P.Value, "fdr")
	df
})
df2 = do.call(rbind, df2)

df3 = lapply( unique(df2$Module), function(mod){

	message(mod)
	# combine p-values with Fisher's method
	p.meta = sumlog(df2$P.Value[df2$Module == mod])$p

	data.frame(Module = mod, P.Value = p.meta)
} )
df3 = do.call(rbind, df3)
df3 = df3[!is.na(df3$P.Value),]
df3$FDR = qvalue(c(1,df3$P.Value))$qvalues[-1]

df3$FDR = p.adjust(df3$P.Value, "fdr")
```

@@

```{r testing.Dx}
# Hypothesis testing     
df_test.Dx = test_differential_correlation(resid.add[[resVersion]], C.diff.discovery, dynamicColors.Dx, METADATA, variable, useSLED=TRUE)  
```
